Machine-learned embedded atom method

### 2019-10-16 doc/papers/ml-eam/manuscript.tex
Add more data.

@@

% Table \ref{table:parameters} shows the optimization results. All these 
% minimization tasks include energy, force and stress terms in their total losses.
% The $\chi_{\mathrm{f}}$ in Equation \ref{eq:loss} is set to 10 and 
% $\chi_{\mathrm{s}}$ is fixe to 80. In this paper, the superscript tag 'old' 
% denotes the original Zjw04, 'res' means restricted optimization and 'unres' 
% means unrestricted optimization. Here 'unrestricted' indicates the parameter 
% $r_e$ will be treated as a common adjustable variable.

% Table \ref{table:MAE} demonstrates the prediction errors of the machine learned
% EAM models and reference models.

% \begin{table*}[h]
% \centering
% \begin{tabular}{lcccccccc}
% \hline
%     & Ni$^{\mathrm{old}}$ & Ni & Ni$^{\mathrm{alloy}}$ 
%     & Mo$^{\mathrm{old}}$ & Mo & Mo$^{\mathrm{alloy}}$ \\
% \hline
% $r_e$ & 2.488746 & 2.124480 & & 2.728100 & & \\
% $f_e$ & 2.007018 & 2.633256 & & 2.723710 & & \\
% $\rho_e$ & 27.562015 & 27.233315 & \\ 
% $\rho_s$ & 27.930410 & 26.392414 &\\
% $\alpha$ & 8.383453 & 8.452753 & \\
% $\beta$ & 4.471175 & 3.285651 & \\
% $A$ & 0.429046 & 0.9802988 & \\
% $B$ & 0.633531 & 0.8919016 & \\
% $\kappa$ & 0.443599 & 0.5685785 & \\
% $\lambda$ & 0.820658 & 1.1653832 & \\
% $F_{n0}$ & -2.693513 & -3.4354472 & \\
% $F_{n1}$ & -0.076445 & 0.3544341 & \\
% $F_{n2}$ & 0.241442 & -2.5563858 & \\
% $F_{n3}$ & -2.375626 & -7.1984844 & \\
% $F_{0}$ & -2.70 & -3.236908 & \\
% $F_{1}$ & 0 & 1.4576268 & \\
% $F_{2}$ & 0.265390 & 2.1785288 & \\
% $F_{3}$ & -0.152856 & -1.642411 & \\
% $\eta$ & 0.469000 & 4.305329 & \\
% $F_e$ & -2.699486 & -3.6163342 & \\
% \hline
% \end{tabular}
% \caption{\label{table:parameters} The original (labeled as 'old'), elemental and 
% alloy parameters.}
% \end{table*}

\begin{table*}[h]
\centering
\begin{tabular}{lcccccccc}
\hline
    & Model & Mo & Ni$_4$Mo & Ni$_3$Mo & Ni$_{\mathrm{Mo}}$ & Mo$_{\mathrm{Ni}}$ 
    & Ni & Overall \\
\hline
Energy (meV/atom) & SNAP & 16.2 & 4.0 & 5.2 & 22.7 & 33.9 & 7.9 & 22.5 \\
    & EAM & 58.9 & 211.2 & 255.6 & 46.5 & 147.6 & 10.6 & 117.2 \\
    & \color{red} ML-EAM & \color{red} 45.0 & \color{red} 10.6 
    & \color{red} 7.1 & \color{red} 39.0 & \color{red} 29.8 & \color{red} 10.4 
    & \color{red} 27.4 \\
    & NN (esf) & 30.0 & 6.1 & 9.0 & 16.6 & 26.2 & 7.8 & 19.1 \\
\hline
Force (eV/\AA) & SNAP & 0.29 & 0.14 & 0.16 & 0.13 & 0.55 & 0.11 & 0.23 \\
& EAM & 0.31 & 0.20 & 0.19 & 0.21 & 0.57 & 0.06 & 0.26 \\
& \color{red} ML-EAM & \color{red} 0.31 & \color{red} 0.17 & \color{red} 0.15 
& \color{red} 0.23 & \color{red} 0.18 & \color{red} 0.09 & \color{red} 0.17 \\
& NN (esf) & 0.36 & 0.10 & 0.11 & 0.08 & 0.16 & 0.06 & 0.12 \\
% \hline
% Stress (GPa) & Mo SNAP & \textbf{0.87} & & & & & & \\
% & Mo SFNN & 1.00 & & & & & & \\
% & Ni-Mo SFNN & 5.77 & \textbf{1.72} & 1.74 & 1.45 & 3.75 & 1.97 & 2.83 \\
% & Ni-Mo SFNN (esf) & \textbf{1.84} & 2.05 & \textbf{1.38} & \textbf{0.57} & 
%     \textbf{1.22} & \textbf{1.91} & \textbf{1.27} \\
\hline
\end{tabular}
\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom) and forces (eV/\AA) 
relative to DFT.}
\end{table*}

\begin{table*}[h]
\centering
\begin{tabular}{lccccc}
\hline
    & DFT & Ni-Mo SNAP & ML-EAM & EAM & Experiment \\
\hline
Mo \\
$c_{11}$ & 472 & 475 (0.6\%) & 477 (1.1\%) & 457 (-3.2\%) & 479 \\
$c_{12}$ & 158 & 163 (3.2\%) & 166 (5.1\%) & 168 (6.3\%) & 165 \\
$c_{44}$ & 106 & 111 (4.7\%) & 101 (-4.7\%) & 116 (9.4\%) & 108 \\
$B_{\mathrm{VRH}}$ & 263 & 267 (1.5\%) & 270 (2.7\%) & 264 (0.4\%) & 270 \\
$G_{\mathrm{VRH}}$ & 124 & 127 (2.4\%) & 127 (2.4\%) & 127 (2.4\%) & 125 \\
$\mu$ & 0.30 & 0.29 (-3.3\%) & 0.31 (3.3\%) & 0.29 (-3.3\%) & 0.30 \\
\hline
Ni \\
$c_{11}$ & 276 & 269 (-2.5\%) & 268 (-2.9\%) & 248 (-10.1\%) & 261 \\
$c_{12}$ & 159 & 150 (-5.7\%) & 165 (3.8\%) & 147 (-7.5\%) & 151 \\
$c_{44}$ & 132 & 135 (2.3\%) & 116 (-12.1\%) & 125 (-5.3\%) & 132 \\
$B_{\mathrm{VRH}}$ & 198 & 190 (-4.0\%) & 200 (1.0\%) & 181 (-8.6\%) & 188 \\
$G_{\mathrm{VRH}}$ & 95 & 97 (2.1\%) & 84 (-11.6\%) & 87 (-8.4\%) & 479 \\
$\mu$ & 0.29 & 0.28 (-3.4\%) & 0.31 (6.8\%) & 0.29 (0.0\%) & 0.29 \\
\hline
Ni$_3$Mo \\
$c_{11}$ & 385 & 420 (9.1\%) & 430 (11.7\%) & 195 (-49.4\%) & \\
$c_{12}$ & 166 & 197 (18.7\%) & 187 (12.7\%) & 98 (-41.0\%) & \\
$c_{13}$ & 145 & 162 (11.7\%) & 180 (24.1\%) & 98 (-32.4\%) & \\
\color{blue} $c_{23}$ & 131 & 145 (10.7\%) & 210 (60.3\%) & 107 (-18.3\%) & \\
$c_{22}$ & 402 & 360 (-10.4\%) & 457 (13.7\%) & 98 (-75.6\%) & \\
\color{blue} $c_{33}$ & 402 & 408 (-1.5\%) & 412 (2.5\%) & 295 (-26.6\%) & \\
\color{blue} $c_{66}$ & 94 & 84 (-10.5\%) & 27 (-71.3\%) & 36 (-61.7\%) & \\
$B_{\mathrm{VRH}}$ & 230 & 243 (5.7\%) & 280 (21.7\%) & 156 (-32.2\%) &  \\
$G_{\mathrm{VRH}}$ & 89 & 100 (12.4\%) & 66 (-25.8\%) & 61 (-31.5\%) & \\
$\mu$ & 0.33 & 0.32 (-3.0\%) & 0.39 (18.2\%) & 0.33 (0.0\%) & \\
\hline
Ni$_4$Mo \\
$c_{11}$ & 300 & 283 (-5.7\%) & 278 (-7.3\%) & 172 (-42.7\%) & \\
$c_{12}$ & 186 & 179 (-3.8\%) & 184 (-1.1\%) & 158 (-15.1\%) & \\
$c_{22}$ & 313 & 326 (4.2\%) & 278 (-11.2\%) & 158 (-49.5\%) & \\
\color{blue} $c_{23}$ & 166 & 164 (-1.2\%) & 230 (38.6\%) & 80 (-51.8\%) & \\
\color{blue} $c_{66}$ & 130 & 126 (-3.1\%) & 87 (-33.1\%) & 125 (-3.8\%) & \\
$B_{\mathrm{VRH}}$ & 223 & 220 (-1.3\%) & 233 (10.5\%) & 161 (-27.8\%) & \\
$G_{\mathrm{VRH}}$ & 91 & 95 (4.4\%) & 57 (37.4\%) & -156 (-162\%) & \\
$\mu$ & 0.33 & 0.31 (-6.1\%) & 0.39 (18.2\%) & 0.70 (112\%) & \\
\hline
\end{tabular}
\caption{\label{table:NiMo_elastic_constants}
Comparion of elastic constants ($c_{ij}$, GPa), Voigt-Reuss-Hill bulk modulus 
($B_{\mathrm{VRH}}$, GPa), Voigt-Reuss-Hill shear modulus ($G_{\mathrm{VRH}}$, 
GPa) and homogeneous Poisson's ratio ($\mu$) for fcc Ni, fcc Mo and binary 
alloys Ni$_{3}$Mo and Ni$_{4}$Mo.
}
\end{table*}

>>>>

The optimized parameters are listed in the appendix.

@@

\begin{table*}[h]
\centering
\begin{tabular}{lcccccccc}
\hline
                  & Model  & Mo   & Ni$_4$Mo & Ni$_3$Mo & Mo$_{\mathrm{Ni}}$ & Ni$_{\mathrm{Mo}}$ & Ni   & Overall \\
\hline
Energy (meV/atom) & SNAP   & 16.2 & 4.0      & 5.2      & 22.7               & 33.9               & 7.9  & 22.5    \\
                  & EAM    & 58.9 & 211.2    & 255.6    & 46.5               & 147.6              & 10.6 & 117.2   \\
                  & ML-EAM & 30.4 & 11.1     & 8.6      & 29.8               & 33.9               & 11.6 & 26.2    \\
                  & ML-ADP & 36.9 & 5.1      & 4.8      & 21.7               & 22.8               & 13.3 & 19.6    \\
\hline
Force (eV/\AA)    & SNAP   & 0.29 & 0.14     & 0.16     & 0.13               & 0.55               & 0.11 & 0.23    \\
                  & EAM    & 0.40 & 0.20     & 0.19     & 0.21               & 0.57               & 0.06 & 0.26    \\
                  & ML-EAM & 0.33 & 0.24     & 0.19     & 0.25               & 0.35               & 0.08 & 0.23    \\
                  & ML-ADP & 0.45 & 0.16     & 0.15     & 0.14               & 0.35               & 0.08 & 0.20    \\
\hline
\end{tabular}
\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom) and forces (eV/\AA) 
relative to the DFT on the entire Mo-Ni dataset.}
\end{table*}

\begin{table*}[h]
\centering
\begin{tabular}{lccccc}
\hline
                   & DFT  & SNAP          & EAM           & ML-EAM        & ML-ADP        \\
\hline
Ni$_3$Mo \\
$c_{11}$           & 385  & 420 (9.1\%)   & 195 (-49.4\%) & 403 (4.7\%)   & 374 (-2.9\%)  \\
$c_{12}$           & 166  & 197 (18.7\%)  & 98 (-41.0\%)  & 208 (25.3\%)  & 160 (-3.6\%)  \\
$c_{13}$           & 145  & 162 (11.7\%)  & 98 (-32.4\%)  & 230 (58.6\%)  & 176 (21.4\%)  \\
$c_{22}$           & 402  & 360 (10.7\%)  & 351 (-12.7\%) & 443 (10.2\%)  & 386 (-4.0\%)  \\
$c_{23}$           & 131  & 145 (-10.4\%) & 107 (13.7\%)  & 272 (107.6\%) & 214 (63.3\%)  \\
$c_{33}$           & 402  & 408 (-10.4\%) & 295 (13.7\%)  & 474 (17.9\%)  & 398 (-0.5\%)  \\
$c_{44}$           & 94   & 84 (-10.4\%)  & 36 (13.7\%)   & 25 (-73.4\%)  & 52 (-44.6\%)  \\
$B_{\mathrm{VRH}}$ & 230  & 243 (5.7\%)   & 156 (-32.2\%) & 302 (31.3\%)  & 250 (8.7\%)   \\
$G_{\mathrm{VRH}}$ & 89   & 100 (12.4\%)  & 61 (-31.5\%)  & 57 (36.0\%)   & 66 (25.8\%)   \\
$\mu$              & 0.33 & 0.32 (-3.0\%) & 0.33 (0.0\%)  & 0.41 (24.2\%) & 0.38 (15.1\%) \\
\hline
Ni$_4$Mo \\
$c_{11}$           & 300  & 283 (-5.7\%)  & 172 (-42.7\%) & 282 (-6.0\%)  & 342 (14.0\%)  \\
$c_{12}$           & 186  & 179 (-3.8\%)  & 158 (-15.1\%) & 125 (-32.8\%) & 217 (16.7\%)  \\
$c_{22}$           & 313  & 326 (4.2\%)   & 158 (-49.5\%) & 282 (-10.0\%) & 342 (9.3\%)   \\
$c_{23}$           & 166  & 164 (-1.2\%)  & 80 (-51.8\%)  & 156 (-6.0\%)  & 232 (39.8\%)  \\
$c_{44}$           & 130  & 126 (-3.1\%)  & 125 (-3.8\%)  & 136 (4.6\%)   & 117 (-10.0\%) \\
$B_{\mathrm{VRH}}$ & 223  & 220 (-1.3\%)  & 161 (-27.8\%) & 178 (-20.1\%) & 257 (15.2\%)  \\
$G_{\mathrm{VRH}}$ & 91   & 95 (4.4\%)    & -156 (-162\%) & 80 (-12.1\%)  & 79 (-13.2\%)  \\
$\mu$              & 0.33 & 0.31 (-6.1\%) & 0.70 (112\%)  & 0.31 (-6.1\%) & 0.36 (9.1\%)  \\
\hline
\end{tabular}
\caption{\label{table:NiMo_elastic_constants}
Comparion of elastic constants ($c_{ij}$, GPa), Voigt-Reuss-Hill bulk modulus 
($B_{\mathrm{VRH}}$, GPa), Voigt-Reuss-Hill shear modulus ($G_{\mathrm{VRH}}$, 
GPa) and homogeneous Poisson's ratio ($\mu$) for fcc Ni, fcc Mo and binary 
alloys Ni$_{3}$Mo and Ni$_{4}$Mo.
}
\end{table*}
